Working Title - CUT Research Paper

### 2019-04-15 CUT/paper.tex
Finished Reference Materials section

>>>>

The effects of Open, Closed, and Cheatsheet exams on retention were measured by~\cite{gharib2012cheat} in an Introductory Psychology class. Across sections, students were given either an Open Book, Closed Book, or Cheatsheet exam. There were $99$ students participating in the study, and they were divided evenly into the three exam formats. Two weeks after writing a midterm with their designated exam format, the students participating in the study were given a surprise quiz to measure retention of the material from the exam. They found that there were no significant differences between retention across exam formats, despite scores on Open Book and Cheatsheet exams being higher than Closed Book exams.
In an Introduction to Statistics course~\cite{block2012discussion} sought to compare the use of Closed Book, Open Book, and Cheatsheet exams. Over the course of four different semesters, Block varied the exam format and measured student performance and perceptions of the course. In Fall $2006$, the exam format was a traditional Closed Book exam. In Spring $2007$, it was an Open Book exam, and again in Fall $2007$. The difference being, in Fall $2007$, the instructor emphasized to the students that the Open Book exam would be more challenging than a corresponding Closed Book exam and they shoud prepare accordingly using by trying for a deeper understanding of the material. Finally, in Spring $2008$, the Cheatsheet format was tried. Students were allowed to put as much information as they could fit on a typically index card and bring that into the exam with them. Their results showed higher performance on the Closed Book and Cheatsheet exams, and lower performance on the Open Book exams. The students preferred Open Book exams, except when they were told that they would be more difficult exams. The Cheatsheet exam reigned supreme, having comparable student enjoyment to the first semester of Open Book exams, and strong student preparation for the exams in line with what was seen for Closed Book exams. The cheatsheet itself encourages good study habits among students, forcing them to summarize and prioritze content, deciding what is truly important to write down.
